The classical mutual information in mean-field spin glass models

### 2015-06-23 sk_model_v16.tex
revised-23/06/2015

%##########################################################################

\section{Monte Carlo method to calculate the classical R\'enyi entropies}
\label{mc-method}

@@

>>>>

%##########################################################################
\section{Monte Carlo method to calculate the classical R\'enyi entropies}
\label{mc-method}

@@

%##########################################################################
\section{The critical temperature}
\label{binder}

In this section we numerically determine the critical temperature $T_c$ of the 
paramagnetic-glassy transition in the S-K model on the booklet. We restrict 
ourselveses the $2$-sheets booklet with fixed aspect ratio (cf. Eq.~\eqref{a-ratio}) 
$\omega=1/4$.

Given two identical, i.e., with the same disorder realization, and independent 
copies of the booklet, the overlap order parameter $q_i$ is defined as 
%
\begin{equation}
q\equiv\frac{1}{2N}\sum\limits_{i}\langle S_i^{(r,1)}S_i^{(r,2)}\rangle,
\end{equation}
%
where $S_i^{(r,1)}$ and $S_i^{(r,2)}$ are the spins living on the two copies 
of the booklet and $r=1,2$ labels the booklet sheets in each copy. The 
angular brackets $\langle\cdot\rangle$ denote the thermal average at 
fixed disorder realization. 
The overlap Binder cumulant $U_4$, which is defined as 
%
\begin{equation}
U_4\equiv \frac{1}{2}\left(3-\frac{[\langle q^4\rangle]}{[\langle q^2\rangle]^2}
\right)
\end{equation}
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\includegraphics*[width=0.87\linewidth]{./draft_figs/Binder}
\caption{ 
}
\label{binder-fig}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
